---
title: "Alcohol vs Seat choice"
author: "Lele"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
I can see that the people sitting middle is the highest compared to the ones sitting in the front and back. Middle (89), Front (40), and Back(36). The standard deviation for the highest is (12.580471). The middle is next with (6.225381) and the front has (3.806013).
## Inferential Tests

## Conclusions


